The Space of Feasible Execution Times for Asynchronous Periodic Task Systems using Definitive Idle Times

### 2013-09-16 dit-paper_ieee.tex
review 3 : added todo comments, fixed equations

\begin{abstract}
	Sensitivity analysis for real-time systems provides efficient methods to determine feasibility
	conditions in the case of small changes in task parameters, such as when porting a system to a
	different platform. The C-space describes the set of execution times for which
	a system is feasible. This paper extends previous works to generalize the
	description of the C-space for Earliest Deadline First scheduling to systems
	with initial task offsets. The feasibility gain offered by offsets is then
	expressed as the volume ratio between the C-space of an asynchronous system and
	its corresponding synchronous system. The problem requires solving multiple
	similar instances of the Chinese Remainder Problem, for which an algorithm
	efficient in this context is provided.
\end{abstract}

@@

\section{Related works}
\label{sct:relatedWorks}
	\subsection{Model}
		We consider a discrete timeline and tasks systems $\tau$ comprised of periodic
		tasks with constrained deadlines on uniprocessor platforms. Each task
		$\tau_i$ is represented by a tuple $(O_i, C_i, D_i, T_i)$ where $O_i$ is the offset value,
		$C_i$ the WCET, $D_i$ the relative deadline and $T_i$ the period.
		The constrained deadline property implies that $\forall i,\; D_i \leq T_i$. In
		the following, we differentiate between \emph{synchronous systems} (where $O_i
		= 0 \; \forall i$) and \emph{asynchronous systems} (which are not synchronous).

@@

		As in the synchronous case, the problem of existence of the FPDIT
		can be written as a system of modular equations:
		\[
			\begin{array}{l}
				\exists ? \; t_d \; s.t. \; \forall \tau_i \in \tau \; :\\
				\left\{
					\begin{array}{l}
						t_d > O_i \\
						t_d - O_i \equiv a_i \; (mod \; T_i) \\
						a_i \in [D_i, T_i]
					\end{array}
				\right.
			\end{array}
		\]

@@

	\subsection{Solving the modular system}
		The existence conditions of	Section~\ref{sct:FPDITexist} can directly be used to calculate the value of
		the FPDIT (if any), because for a given set of $a_i$ values they are
		very similar to an instance of the Chinese Remainder Problem (CRP), which is
		easily solved using Gauss's CRP solving method for non-coprime moduli
		\cite{gauss1965disquisitiones}.

@@

>>>>

\begin{abstract}
	Sensitivity analysis for real-time systems provides efficient methods to determine feasibility
	conditions in the case of small changes in task parameters, such as
	different WCET values when porting a system to a different platform. The C-space describes the set of execution
	times for which a system is feasible, which allows system designers to quickly
	find the best platform for a given task set. This paper extends previous works
	to generalize the description of the C-space for Earliest Deadline First
	scheduling to systems with initial task offsets. The feasibility gain offered
	by offsets is then expressed as the volume ratio between the C-space of an
	asynchronous system and its corresponding synchronous system. The problem
	requires solving multiple similar instances of the Chinese Remainder Problem,
	for which an algorithm efficient in this context is provided.
\end{abstract}

@@

\section{Related works}
\label{sct:relatedWorks}

%Review 3 : add map of literature

	\subsection{Model}
		We consider a discrete timeline and tasks systems $\tau$ comprised of periodic
		tasks with constrained deadlines on uniprocessor platforms. Each task
		$\tau_i$ is represented by a tuple $(O_i, C_i, D_i, T_i)$ where $O_i$ is the offset value,
		$C_i$ the WCET, $D_i$ the relative deadline and $T_i$ the period.
		The constrained deadline property implies that $\forall i,\; D_i \leq T_i$. In
		the following, we differentiate between \emph{synchronous systems} (where $O_i
		= 0 \; \forall i$) and \emph{asynchronous systems} (which are not synchronous).

@@

		As in the synchronous case, the problem of existence of the FPDIT
		can be written as a system of modular equations:
		\[
			\begin{array}{l}
				\exists ? \; t_d \; s.t. \; \forall \tau_i \in \tau, \exists a_i \in [D_i,
				T_i] \; :\\
				\left\{
					\begin{array}{l}
						t_d > O_i \\
						t_d - O_i \equiv a_i \; (mod \;	T_i)
						\\
					\end{array}
				\right.
			\end{array}
		\]

@@

	\subsection{Solving the modular system}
		The existence conditions of	Section~\ref{sct:FPDITexist} can directly be used to calculate the value of
		the FPDIT (if any), because for a given set of $a_i$ values the problem of
		finding the corresponding DIT is an instance of the Chinese Remainder Problem
		(CRP), which is easily solved using Gauss's CRP solving method for non-coprime
		moduli \cite{gauss1965disquisitiones}.

		%Review 3 : explain Gauss algorithm

@@

		%Review 3 : add formal complexity assessment of this algorithm
